---
title: "Systematic map of meta-analyses related to sexual selection"
author: "Pietro Pollo"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    theme: united
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

```{r Load packages and data, message=FALSE, warning=FALSE, include=TRUE}
if (!require("pacman")) {install.packages("pacman")}
pacman::p_load(broom,
               broom.mixed,
               emmeans,
               ggtext,
               janitor,
               lme4,
               multcomp,
               multcompView,
               patchwork,
               tidyverse)

# load data ----
df_articles <- read_csv("per_article.csv") %>% 
  mutate(article_type = as.factor(str_to_sentence(article_type)))
df_references <- read_csv("per_reference.csv")
df_quotes <- read_csv("per_quote.csv")
```


# Overview of articles and journals

## Number of articles

### Total
```{r message=FALSE, warning=FALSE}
df_articles %>% 
  count()
```

### Manually inspected
```{r message=FALSE, warning=FALSE}
df_articles %>% 
  count(manually_verified,
        include_analysis)
```

## Number of journals

### Total

```{r message=FALSE, warning=FALSE}
df_articles %>% 
  count(source_title) %>%
  count()
```

### Manually inspected

```{r message=FALSE, warning=FALSE}
df_articles %>% 
  filter(manually_verified) %>% 
  count(source_title) %>%
  count()
```

## Number of articles retrieved that cited at least one meta-analysis

```{r message=FALSE, warning=FALSE}
df_articles %>% 
  filter(n_all_refs_lens > 0) %>% 
  group_by(detected_meta = n_meta_refs_auto > 0) %>% 
  summarise(n = n(),
            prop = n / nrow(df_articles %>% 
                              filter(n_all_refs_lens > 0)))

```

# True meta-references

## Proportion of true meta-references from all meta-references

```{r message=FALSE, warning=FALSE}
df_articles %>% 
  filter(include_analysis) %>%
  summarise(prop = sum(n_true_meta_refs) / sum(n_meta_refs_manual))
```

## Model on absolute number of true meta-references

```{r message=FALSE, warning=FALSE}
glmer_n_true_neg_bin <-
  df_articles %>% 
  filter(include_analysis) %>% 
  glmer.nb(data = .,
           n_true_meta_refs ~ 
             article_type - 1 +
             (1|issn))

summary(glht(glmer_n_true_neg_bin,
             linfct = mcp(article_type = "Tukey")))

cld(glht(glmer_n_true_neg_bin,
         linfct = mcp(article_type = "Tukey")),
    test = adjusted("none"),
    letters = Letters)
```

## Model on all references

```{r message=FALSE, warning=FALSE}
glmer_n_all_neg_bin <-
  df_articles %>% 
  filter(include_analysis) %>% 
  glmer.nb(data = .,
           n_all_refs_wos ~ 
             article_type - 1 +
             (1|issn))

cld(glht(glmer_n_all_neg_bin,
         linfct = mcp(article_type = "Tukey")),
    test = adjusted("none"),
    letters = Letters)

summary(glht(glmer_n_all_neg_bin,
             linfct = mcp(article_type = "Tukey")))

```

## Model on relative number of true meta-references to all references

```{r message=FALSE, warning=FALSE}
glmer_rel_true <-
  df_articles %>% 
  filter(include_analysis) %>% 
  glmer(data = .,
        cbind(n_true_meta_refs,
              n_all_refs_wos - n_true_meta_refs) ~ 
          article_type - 1 +
          (1|issn),
        family = "binomial")


emm <- emmeans(glmer_rel_true, 
               ~ article_type, 
               type = "response")
summary(emm)

cld(glht(glmer_rel_true,
         linfct = mcp(article_type = "Tukey")),
    test = adjusted("none"),
    letters = Letters)

summary(glht(glmer_rel_true,
             linfct = mcp(article_type = "Tukey")))
```

## Fig. 2

```{r message=FALSE, warning=FALSE}
# fig 2a ----
fig_2a <-
  df_articles %>% 
  filter(include_analysis) %>% 
  ggplot(aes(x = article_type,
             y = n_true_meta_refs)) +
  geom_boxplot(outliers = F) +
  geom_jitter(height = 0,
              width = 0.2,
              alpha = 0.3) +
  geom_point(data = tidy(glmer_n_true_neg_bin) %>%
               mutate(corrected_est = exp(estimate),
                      term = str_remove(term,
                                        "article_type")) %>% 
               filter(is.na(group)),
             aes(x = term,
                 y = corrected_est),
             col = "red",
             size = 2) +
  annotate("text",
           x = c(1:6),
           y = -1,
           label = c("a",
                     "b",
                     "a",
                     "ab",
                     "a",
                     "a")) +
  annotate("text",
           x = c(1:6),
           y = 19,
           label = paste0("N = ",
                          df_articles %>% 
                            filter(include_analysis) %>% 
                            count(article_type) %>% 
                            pull(n))) +
  labs(x = "Article type",
       y = "Number of true meta-references") +
  scale_y_continuous(limits = c(-1, 21)) +
  expand_limits(y = 20) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(margin = margin(r = 0.3, unit = "cm"),
                                    size = 12),
        axis.text = element_text(size = 9),
        plot.tag.position = c(0.14, 0.95))

# fig 2b ----
fig_2b <-
  df_articles %>% 
  filter(include_analysis) %>% 
  ggplot(aes(x = article_type,
             y = n_all_refs_wos)) +
  geom_boxplot(outliers = F) +
  geom_jitter(height = 0,
              width = 0.2,
              alpha = 0.3) +
  geom_point(data = tidy(glmer_n_all_neg_bin) %>%
               mutate(corrected_est = exp(estimate),
                      term = str_remove(term,
                                        "article_type")) %>% 
               filter(is.na(group)),
             aes(x = term,
                 y = corrected_est),
             col = "red",
             size = 2) +
  annotate("text",
           x = c(1:6),
           y = -1,
           label = c("a",
                     "bc",
                     "ac",
                     "ac",
                     "b",
                     "a")) +
  labs(x = "Article type",
       y = "Total number of references") +
  scale_y_continuous(limits = c(-1, 550),
                     breaks = seq(0, 500, 100)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(margin = margin(r = 0.3, unit = "cm"),
                                    size = 12),
        axis.text = element_text(size = 9),
        plot.tag.position = c(0.14, 0.95))

# fig 2c ----
fig_2c <- 
  df_articles %>% 
  filter(include_analysis) %>% 
  ggplot(aes(x = article_type,
             y = rel_true_meta_refs)) +
  geom_boxplot(outliers = F) +
  geom_jitter(height = 0,
              width = 0.2,
              alpha = 0.3) +
  geom_point(data = as.data.frame(emmeans(glmer_rel_true,
                                          ~article_type, 
                                          type = "response")),
             aes(x = article_type,
                 y = prob),
             col = "red",
             size = 2) +
  annotate("text",
           x = c(1:6),
           y = -0.02,
           label = c("a",
                     "b",
                     rep("abc", 2),
                     "c",
                     "abc")) +
  labs(x = "Article type",
       y = "Proportion of true meta-references\namong all references") +
  scale_y_continuous(limits = c(-0.02, 0.2)) +
  theme_classic() +
  theme(axis.title.x = element_text(margin = margin(t = 0.3, unit = "cm"),
                                    size = 12),
        axis.title.y = element_text(margin = margin(r = 0.3, unit = "cm"),
                                    size = 12),
        axis.text = element_text(size = 9),
        plot.tag.position = c(0.14, 0.95))

(fig_2 <-
  fig_2a + 
  fig_2b + 
  fig_2c + 
  plot_layout(nrow = 3) +
  plot_annotation(tag_levels = "A"))

# ggsave("fig_2.jpg",
#        fig_2,
#        bg = "white",
#        dpi = 600,
#        width = 7,
#        height = 7*1.41*0.85,
#        units = "in")
```

## Fig. 3

```{r message=FALSE, warning=FALSE}
glmer_jif_prop <-
  df_articles %>% 
  filter(include_analysis) %>% 
  mutate(jif_2022_s = scale(jif_2022)) %>% 
  glmer(data = .,
        cbind(n_true_meta_refs,
              n_all_refs_wos - n_true_meta_refs) ~ 
          jif_2022_s +
          (1|issn) +
          (1|article_type),
        family = "binomial")

summary(glmer_jif_prop)

emmeans_df <- 
  tibble(as.data.frame(emmeans(glmer_jif_prop,
                               ~ jif_2022_s,
                               at = list(jif_2022_s = seq(min(scale(df_articles %>% 
                                                                      filter(include_analysis) %>% 
                                                                      pull(jif_2022))), 
                                                          max((scale(df_articles %>% 
                                                                       filter(include_analysis) %>% 
                                                                       pull(jif_2022)))), 
                                                          length.out = 100)),
                               type = "response"))) %>% 
  mutate(jif_2022 = (jif_2022_s * 
                       sd(df_articles %>% 
                            filter(include_analysis) %>% 
                            pull(jif_2022))) +
           mean(df_articles %>% 
                  filter(include_analysis) %>% 
                  pull(jif_2022)))

## fig. 3 ----

(fig_3 <- 
  df_articles %>% 
  filter(include_analysis) %>% 
  # mutate(jif_2022_s = scale(jif_2022)) %>% 
  ggplot(aes(x = jif_2022,
             y = rel_true_meta_refs)) +
  geom_jitter(height = 0,
              width = 0.2,
              alpha = 0.3) +
  geom_smooth(data = emmeans_df,
              aes(x = jif_2022,
                  y = prob),
              col = "red") +
  geom_smooth(data = emmeans_df,
              aes(x = jif_2022,
                  y = asymp.LCL),
              linetype = "dashed",
              col = "red",
              alpha = 0.3) +
  geom_smooth(data = emmeans_df,
              aes(x = jif_2022,
                  y = asymp.UCL),
              linetype = "dashed",
              col = "red",
              alpha = 0.3) +
  labs(x = "Clarivate's 2022 journal impact factor",
       y = "Proportion of true meta references\namong all references",
       col = "Article type") +
  theme_classic() +
  theme(axis.title.x = element_text(margin = margin(t = 0.3, unit = "cm"),
                                    size = 12),
        axis.title.y = element_text(margin = margin(r = 0.3, unit = "cm"),
                                    size = 12),
        axis.text = element_text(size = 9)))

# ggsave("fig_3.jpg",
#        fig_3,
#        bg = "white",
#        dpi = 600,
#        width = 7,
#        height = 7*1.41*0.85*0.5,
#        units = "in")


```

# Meta-references per manuscript section

```{r message=FALSE, warning=FALSE}
x <-
  df_references %>% 
  distinct(article_id,
           meta_ref_id,
           meta_ref_section_adj,
           .keep_all = T) %>%
  left_join(df_articles %>% 
              dplyr::select(article_id,
                            article_type)) %>%
  filter(is_meta_ref_meta_analysis,
         !is.na(meta_ref_section_adj),
         meta_ref_section_adj != "other",
         article_type != "invalid") %>%
  count(article_type,
        meta_ref_section_adj) %>% 
  pivot_wider(names_from = meta_ref_section_adj,
              values_from = n) %>% 
  mutate(methods = replace_na(methods, 0),
         total = introduction + methods + `results/discussion/conclusion`,
         prop_intro = introduction / total,
         prop_methods = methods / total,
         prop_res = `results/discussion/conclusion` / total)

```

## Model for introduction section

```{r message=FALSE, warning=FALSE}
glm_introduction <-
  x %>% 
  glm(data = .,
      cbind(introduction,
            total - introduction) ~ 
        article_type - 1,
      family = "binomial")

cld(glht(glm_introduction,
         linfct = mcp(article_type = "Tukey")),
    test = adjusted("none"),
    letters = Letters)

summary(glht(glm_introduction,
             linfct = mcp(article_type = "Tukey")))
```

## Model for methods section

```{r message=FALSE, warning=FALSE}
glm_methods <-
  x %>% 
  glm(data = .,
      cbind(methods,
            total - methods) ~ 
        article_type - 1,
      family = "binomial")

cld(glht(glm_methods,
         linfct = mcp(article_type = "Tukey")),
    test = adjusted("none"),
    letters = Letters)

summary(glht(glm_methods,
             linfct = mcp(article_type = "Tukey")))
```

## Model for discusssion section

```{r message=FALSE, warning=FALSE}
glm_discussion <-
  x %>% 
  glm(data = .,
      cbind(`results/discussion/conclusion`,
            total - `results/discussion/conclusion`) ~ 
        article_type - 1,
      family = "binomial")

cld(glht(glm_discussion,
         linfct = mcp(article_type = "Tukey")),
    test = adjusted("none"),
    letters = Letters)

summary(glht(glm_discussion,
             linfct = mcp(article_type = "Tukey")))

```

## Fig. 4

```{r message=FALSE, warning=FALSE}
### fig 4a ----
fig_4a <- 
  df_references %>% 
  distinct(article_id,
           meta_ref_id,
           meta_ref_section_adj,
           .keep_all = T) %>%
  left_join(df_articles %>% 
              dplyr::select(article_id,
                            article_type)) %>%
  filter(is_meta_ref_meta_analysis,
         !is.na(meta_ref_section_adj),
         meta_ref_section_adj != "other",
         article_type != "invalid") %>%
  count(article_type,
        meta_ref_section_adj) %>% 
  group_by(article_type) %>%
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = article_type,
             y = prop,
             group = meta_ref_section_adj,
             fill = meta_ref_section_adj,
             label = n)) +
  geom_col() +
  geom_label(hjust = 0.5,
             position = position_stack(vjust = 0.5),
             col = "black",
             fill = "white",
             label.r = unit(0.4, "lines"),
             label.padding = unit(0.15, "lines"),
             size = 3.5) +
  scale_fill_manual(values = c("grey90", "grey60", "grey30")) +
  scale_y_continuous(breaks = seq(0 , 1, by = 0.2),
                     limits = c(0, 1)) +
  labs(pattern = "Section",
       pattern_angle = "Section",
       pattern_density = "Section",
       pattern_spacing = "Section",
       fill = "Section",
       x = "Article type",
       y = "Proportion of articles") +
  theme_classic() +
  theme(axis.title.x = element_text(margin = margin(t = 0.3, unit = "cm"),
                                    size = 12),
        axis.title.y = element_text(margin = margin(r = 0.3, unit = "cm"),
                                    size = 12),
        axis.text = element_text(size = 9),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 9),
        legend.position = "top",
        plot.tag.position = c(0.13, 0.93))


### fig 4b ----
res_quotes <- 
  df_quotes %>%
  count(reports_any_result,
        reports_quantitative_result,
        reports_limitation) %>% 
  mutate(prop = n/nrow(df_quotes))

fig_4b <-
  res_quotes %>%
  filter(reports_any_result) %>% 
  summarise(n = sum(n),
            value = sum(prop)) %>% 
  bind_rows(res_quotes %>%
              filter(reports_quantitative_result) %>% 
              summarise(n = sum(n),
                        value = sum(prop))) %>% 
  bind_rows(res_quotes %>%
              filter(reports_limitation) %>% 
              summarise(n = sum(n),
                        value = sum(prop))) %>% 
  mutate(x = factor(c("Any result",
                      "Quantitative result",
                      "Limitation"),
                    levels = c("Any result",
                               "Quantitative result",
                               "Limitation"))) %>% 
  ggplot(aes(x = x,
             y = value,
             label = n)) +
  geom_col(fill = "black") +
  geom_label(hjust = 0.5,
             position = position_stack(vjust = 0.5),
             col = "black",
             fill = "white",
             label.r = unit(0.4, "lines"),
             label.padding = unit(0.15, "lines"),
             size = 3.5) +
  scale_y_continuous(breaks = seq(0 , 1, by = 0.2),
                     limits = c(0, 1)) +
  labs(x = "Content type",
       y = "Proportion of quotations") +
  theme_classic() +
  theme(axis.title.x = element_text(margin = margin(t = 0.3, unit = "cm"),
                                    size = 12),
        axis.title.y = element_text(margin = margin(r = 0.3, unit = "cm"),
                                    size = 12),
        axis.text = element_text(size = 9),
        plot.tag.position = c(0.13, 0.95))

### joined figures ----
(fig_4 <-
  fig_4a +
  fig_4b +
  plot_layout(nrow = 2) +
  plot_annotation(tag_levels = "A"))

# ggsave("fig_4.jpg",
#        fig_4,
#        bg = "white",
#        dpi = 600,
#        width = 7,
#        height = 7*1.41*0.6,
#        units = "in")

```

# Quote content

## Proportion of quotes on meta-analyses' results

```{r message=FALSE, warning=FALSE}
df_quotes %>% 
  count(reports_any_result,
        reports_quantitative_result) %>% 
  mutate(prop = n/nrow(df_quotes))

```

## Proportion of quotes on meta-analyses' limitations

```{r message=FALSE, warning=FALSE}

## proportion of quotes about limitation ----
df_quotes %>% 
  count(reports_limitation) %>% 
  mutate(prop = n/nrow(df_quotes))
```

# Efficiency of detecting meta-references

```{r message=FALSE, warning=FALSE}
df_articles %>%
  filter(manually_verified) %>%
  mutate(auto_meta = str_detect(title,
                                "meta-an|metaan|meta-reg|metareg")) %>% 
  count(auto_meta,
        article_type)

tp <- 22
fn <- 25
fp <- 1
tn <- 638

```

## Precision 
```{r message=FALSE, warning=FALSE}

#### precision ----
tp/(tp+fp)

```

## Sensitivity 
```{r message=FALSE, warning=FALSE}

#### sensitivity ----
tp/(tp+fn)

```

## Accuracy
```{r message=FALSE, warning=FALSE}

#### accuracy ----
(tp+tn)/(tp+fp+tn+fn)
```

